---
layout: post
title:  Vectors in mathematics and in codes
date: `r Sys.Date()`
categories: [R_programming, statistics, latex]
---
When a set of data/observations is imported to R, it is usually treated as `vector`. Vector has two mathematical forms as following:  

**column vector**:  
$$ \vec{a} = \begin{bmatrix}
 1\\
 2\\
 3\\
\end{bmatrix} $$  
**row vector**:  
$$ \vec{a} = [ 1\ 2\ 3 ] $$

Default form of vector in R is column vector. More precisely, it is treated as a matrix:  
```{r vector, echo=TRUE, message=FALSE, warning=FALSE}
a <- 1:3
a
class(a)
str(a)
t(a)
```

In a statistical work, we used to calcuate the sum of square (SS) for the deviations to mean. The common equation is like:  
$$ \sum_{i=1}^{n}(Y_{i}-\overline{Y})^2 $$  

This is the fundemental for calculating the variance of this set of data/observations. The equation of variance is like this:  
$$ \frac{\sum_{i=1}^{n}(Y_{i}-\overline{Y})^2}{n} $$  

Because the data/observations are treated as matrix, we are able to have the sum of square by the multiplication of this matrix.  
$$ \mathbf{A'A} = 
\begin{bmatrix} A_1 A_2 A_3 \dots\end{bmatrix}
\times
\begin{bmatrix}
   A_1 \\
   A_2 \\
   A_3 \\
   \vdots
\end{bmatrix}　$$　　

Here are ten observations `r 1:10`, the average of this data is `r mean(1:10)`. Let's have the SS and variance in use of the multiplication of matrix:  
```{r multiplication, echo=TRUE, message=FALSE, warning=FALSE}
SS <- t(1:10 - mean(1:10)) %*% (1:10 - mean(1:10)) 
VAR <- SS/length(1:10)
SS
VAR
```

In R `base` package, the function `var` outputs a sampling variance, not a population variance as above.
```{r base, echo=TRUE, message=FALSE, warning=FALSE}
var(1:10)
```

